---
title: "The Basics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Vectors

Creates a vector of strings
```{r}
v1 = c("foo", "bar", "baz")
```
Gets the first value
Note that R is not 0 indexed
```{r}
v1[1]
```
Creates a vector of numbers
```{r}
v2 = c(1, 2, 3)
```
Concatinate vectors
Note that `paste` concatinates with spaces and `paste0` without spaces
```{r}
paste(v1, v2)
paste0(v1, v2)
```
Generate 10 random numbers from 1 to 100
Note the `FALSE` argument means without replacement
The default is `TRUE` meaning there can be duplicates
```{r}
x = sample(1:100, 10, FALSE)
print(x)
```
The mean can be found in multiple ways
```{r}
mean(x)
sum(x)/length(x)
```
The trim argument is used to cut off a fraction of observations before finding the mean
By default it's 0
```{r}
mean(c(1,2,3,4,5,6,7,8,9,10), 0.2)
```
The `na.rm` argument can remove `NA` values before computing
```{r}
mean(c(1,3,NA,NA,NA))
mean(c(1,3,NA,NA,NA), na.rm=TRUE)   
```
Here are some other functions that can be used on vectors
```{r}
v = c(1,2,3,4,5,6,7,8,9,10)
min(v)
max(v)
```